---
title: "Week 3 assignment"
author: "ZIXIAN LIANG"
date: "2024-02-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1.Please deliver links to an R Markdown file (in GitHub and rpubs.com) with solutions to the problems below.  You may work in a small group, but please submit separately with names of all group participants in your submission.
1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r}
library(tidyverse)
```

Data Acquisition
Input file:"all-ages.csv" from https://github.com/fivethirtyeight/data/tree/master/college-majors


```{r}
url <- 'https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/all-ages.csv'
database <- read_csv(url)
database
```


Then we can look up rows containing key words.


```{r}
majors_containing_data_or_statistics <- database[grep("DATA|STATISTICS", database$Major),]
majors_containing_data_or_statistics
```

2.PLEASE SEE HINT/CLARIFICATION AFTER #4 BELOW. Write code that transforms the data below:
[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"
Into a format like this:
c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")
The two exercises below are taken from R for Data Science, 14.3.5.1 in the on-line version:

--------

First create dataframe.

```{r}
fruit <- c("bell pepper", "bilberry", "blackberry", "blood orange",
          "blueberry", "cantaloupe", "chili pepper", "cloudberry",
          "elderberry", "lime", "lychee", "mulberry",
          "olive", "salal berry")
fruit
```

Once we have dataframe fruit available, then we can use "Paste()" to concatenate.


```{r}
strOut  <- paste("c(", paste0("\"", fruit, "\"", collapse = ", "), ")", collapse = "")
str_view(strOut)
```
3.Describe, in words, what these expressions will match:

1-(.)\1\1

(.) means a single letter, \1 means repeating first letter, so \1\1 means repeating twice

Example "a" in (.)\1\1 format is "aaa";

2-"(.)(.)\\2\\1"

Similar like above, \2 means repeating second letter

Example "ab" in (.)(.)\\2\\1 format is "abba";

3-(..)\1

These parentheses contain two ".", so it check any pairs of letters

Example "ab" in (..)\1 format is "abab";


4-"(.).\\1.\\1"

"." letter inside parentheses will be the same with \1, "." letter without parentheses can be anything.

Example a,b,c is "(a)b1c1" in (.).\\1.\\1 format is "abaca";


5-"(.)(.)(.).*\\3\\2\\1"

New thing in here is ".*", this can be nothing or any lengths of letters

Example "abc" in (.)(.)(.).*\\3\\2\\1 format is "abccba";

Example "abc123" in (.)(.)(.).*\\3\\2\\1 format is "abc123cba";

4.Construct regular expressions to match words that:

```{r}
sample_use <- c("civic", "abab", "transmission")
sample_use
```


Start and end with the same character.

```{r}
str_view(sample_use, "^(.).*\\1$")
```

Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)

```{r}
str_view(sample_use, "(.)(.).*\\1\\2")
```

Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

```{r}
str_view(sample_use, "(.).*\\1.*\\1")
```

